---
title: "Simulated Patient Characteristics at Baseline"
author: "Ting Ma"
date: '`r lubridate::now(tzone= "America/Los_Angeles")`'
framework: bootstrap
highlighter: prettify
output:
  html_document:
    toc: yes
    toc_float: 
      collapsed: false
    code_folding: hide
    highlight: kate
---

<style>
body{
  font-family: 'Oxygen', sans-serif;
  font-size: 16px;
  line-height: 24px;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

.container { width: 1000px; }
h3 {
  background-color: #D4DAEC;
  text-indent: 100px; 
}
h4 {
  text-indent: 100px;
}

g-table-intro h4 {
  text-indent: 0px;
}
</style>



```{r setup, include=FALSE}
library(knitr)
library(pander)
library(janitor)
library(haven)
library(Hmisc)
library(lubridate)
library(grails3r)
library(stringr)
library(plyr)
library(tidyverse)
library(janitor)
library(pander)
library(readxl)
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction   
This simulation is to demonstrate how Rmd can be used to practice reproducible research.
To view the rendered html file, add "https://htmlpreview.github.io/?" to the url.

* Population: simulated subjects    
* Characteristics analyzed:           
    + Sex   
    + Age    

##Input datasets
* input_df.csv


```{r adata, warning=F}

rm(list=ls())

options(stringsAsFactors = FALSE)

my_spec <- cols(
  subjid = col_double(),
  icdat = col_date(format = ""),
  network = col_character(),
  pt_chars = col_character(),
  value = col_character(),
  icdat_rev = col_date(format = ""),
  icdat_rev2 = col_date(format = ""),
  var_lbl = col_character()
)

adsl_care_long <- read_csv("/Users/tma/Desktop/g_demo/Rmd_demo/input_df.csv",
                           col_types = my_spec)

```

##Visualization
```{r func_here}
#customer functions------------------------------------------------------
#my_date <- as.Date(c("2016-01-02", "2016-03-04", "2017-09-08"))

single_year <- function(x){
      y <- if_else(is.na(lag(x)) | !year(lag(x)) == year(x),
                          paste(month(x, label = TRUE), "\n", year(x)),
                          paste(month(x, label = TRUE)))

      return (y)
}

#x <- single_year(my_date)
```

###Sex
```{r p_sex, out.width = "100%"}
#sex-----------------------------------------------------------------
d_sex <- adsl_care_long %>%
      dplyr::filter(pt_chars == "sex") %>%
      # dplyr::mutate(icdat_rev2 = as.Date(paste0(lubridate::year(icdat), "-", lubridate::month(icdat), "-", "1"))) %>%
      dplyr::add_count(pt_chars, network, icdat_rev2) %>%
      dplyr::rename(N = n) %>% 
      dplyr::add_count(pt_chars, network, icdat_rev2, value ) %>%
      dplyr::distinct(icdat_rev2, network, pt_chars, network, value, N, n ) %>%
      dplyr::mutate(pct = n / N)

p_sex <- ggplot(data=d_sex, mapping = (aes(x=icdat_rev2, y=pct))) +
      geom_point(aes(size=n, color=value)) +
      #    scale_x_date(date_breaks = "1 month", date_labels = "%y-%b") +
      scale_fill_brewer(palette="Set3") +
      facet_wrap(~ network, nrow = 10 ) +
      theme(text = element_text(size=11)) +
      scale_size_continuous (breaks = c(20, 100, 200)) +
      theme(legend.position="bottom", legend.title=element_blank())


##fix labels for dates on X axis==
p_sex <- p_sex + scale_x_date(date_breaks = "1 months",
                              labels = single_year) +
      geom_vline(xintercept = as.Date(c("2017-01-01", "2018-01-01")), colour="grey60")

p_sex

```

###Age
```{r p_age, warning=F,  out.width = "100%"}
#age ------------------------------------------------------------------------
d_age <- adsl_care_long %>%
      dplyr::filter(pt_chars == "age")


p_age <- ggplot(data=d_age, mapping = (aes(x=icdat_rev2, y=as.numeric(value), group = icdat_rev2)), na.rm=TRUE) +
      geom_boxplot(color = "#009999") +
      scale_fill_brewer(palette="Set3") +
      facet_wrap (~ network, ncol=1) +
      scale_y_continuous(name="Age", limits=c(10, 100), breaks = seq(0, 100, 10), minor_breaks = NULL) +
      theme(legend.position="bottom")


p_age <- p_age + scale_x_date(date_breaks = "1 months",
                     labels = single_year) +
      geom_vline(xintercept = as.Date(c("2017-01-01", "2018-01-01")), colour="grey60") +
      theme_bw() +
      theme(panel.grid.minor = element_blank(), legend.title=element_blank())

p_age

```


